Grappa: Scalable Computing on Mass-Market Hardware for Irregular, Low-Locality Applications

### 2012-07-23 doc/asplos13/relatedwork.tex
minor edits

\paragraph{Comparable frameworks} Distributed graph processing
frameworks like Pregel \cite{pregel:2010} and Distributed GraphLab
\cite{distgraphlab:vldb12} share similar goals as Grappa. Pregel adopts
a bulk-synchronous parallel (BSP) execution model, which makes it
inefficient on workloads that could prioritize vertices. GraphLab, on
the other hand, schedules vertex computations individually, allowing
prioritization, which gives faster convergence in a variety of iterative
algorithms.  GraphLab, however, imposes a rigid computation model where
programmers must express computation as transformations on a vertex and
its edge list only, with only information from adjacent vertexes. Pregel
is only slightly less restrictive, as the input data can be any vertex
in the graph.  Grappa also supports dynamic parallelism with
asynchronous execution, but parallelism is expressed as tasks or loop
iterations. By comparison, this is a far more general programming model
for irregular computation tasks.

>>>>

\paragraph{Comparable frameworks} Distributed graph processing
frameworks like Pregel \cite{pregel:2010} and Distributed GraphLab
\cite{distgraphlab:vldb12} share similar goals as Grappa. Pregel adopts
a bulk-synchronous parallel (BSP) execution model, which makes it
inefficient on workloads that could prioritize vertices. GraphLab, on
the other hand, schedules vertex computations individually, allowing
prioritization, which gives faster convergence in a variety of iterative
algorithms.  GraphLab, however, imposes a rigid computation model where
programmers must express computation as transformations on a vertex and
its edge list only, with only information from adjacent vertexes. Pregel
is only slightly less restrictive, as the input data can be any vertex
in the graph.  Grappa also supports dynamic parallelism with
asynchronous execution, but parallelism is expressed as tasks or loop
iterations, which is a far more general programming model
for irregular computation tasks.
